\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-23 tex/paper.tex
Added javascript description

\item[Javascript]
\fix Add description

\item[SuperAgent]
\fix Add citation to SuperAgent
is a small HTTP request library which can be used from client-side Javascript or as a node.js
module. It is used to form the requests to the REST API from the front-end, which can be seen in
Figure~\ref{fig:tech_stack} (Arrow 1 and 2).

@@

% \hfill \\ % \label{sec:reflux}
\item[Reflux]~\cite{REFLUX} 
is an idea and a simple library of how to structure your application. It features a unidirectional
dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than for example
Flux~\cite{FLUX}, when using a functional reactive programming style. Reflux is used together with
React for this implementation to define a structure of the flow of data and state changes.

@@

\item[Scala]% \hfill \\ %\label{sec:scala}
is a multi-paradigm programming language. It most commonly runs on the JVM and unlike Java it
supports most functional programming features at the same time as it supports object-oriented
programming~\cite{SCALA}. Scala is used to program the back-end and the Spray toolkit is used with
it to simplify the API.

\item[REST]% \hfill \\ %\label{sec:rest}
stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.

>>>>

\item[Javascript]
is a programming language mainly focussed on running code in web browsers~\cite{JAVASCRIPT}. In this
implementation the ECMAScript 6 (ES6) language specification is used, which adds a lot of syntactic
sugar compared to what usually is called normal JavaScript. An example of such syntactic sugar is
lambda expressions. React and Reflux are both built with JavaScript in mind and is used on top of
JavaScript is this implementation, as can be seen in Figure~\ref{fig:tech_stack}.

\item[SuperAgent]
is a small HTTP request library which can be used from client-side Javascript or as a node.js
module~\cite{SUPERAGENT}. It is used to form the requests to the REST API from the front-end, which
can be seen in Figure~\ref{fig:tech_stack} (Arrow 1 and 2).

@@

\item[Reflux] 
is an idea and a simple library of how to structure your application~\cite{REFLUX}. It features a
unidirectional dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than for example
Flux~\cite{FLUX}, when using a functional reactive programming style. Reflux is used together with
React for this implementation to define a structure of the flow of data and state changes.

@@

\item[Scala]
is a multi-paradigm programming language. It most commonly runs on the JVM and unlike Java it
supports most functional programming features at the same time as it supports object-oriented
programming~\cite{SCALA}. Scala is used to program the back-end and the Spray toolkit is used with
it to simplify the API.

\item[REST]
stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.
